---
title: "Automatic Gating To Singlets"
author: "Hanne Grosemans"
output: github_document
---

# Load packages
```{r}
#source("http://www.bioconductor.org/biocLite.R")
#biocLite("BiocUpgrade")
library(tidyverse)
library(openCyto)
library(flowViz)
library(flowUtils)
library(flowDensity)
library(ggplot2)
library(dplyr)
library(ggcyto)
library(flowWorkspace)
```

#Load fcs file
```{r}
fcsFile <- list.files(path = "FCS/", pattern = ".fcs")
fs <- read.flowSet(fcsFile, path = "FCS/")
fcsFile <- read.FCS("FCS/WT.fcs")
```
#Explore data
```{r}
fcsFile
exprs(fcsFile)[1:10,]
summary(fcsFile)
str(keyword(fcsFile))
summary(fcsFile[,c(2, 8, 17, 23, 26)])
```

#Compensation
Check $SPILLOVER for correct file by changing the x in spillover(fcsFile)[[x]] in the console (only #Single file)
```{r}
#Single file
fcsFile_comp <- compensate(fcsFile, spillover(fcsFile)[[3]])
fcsFile_comp
#All files
comp <- fsApply(fs, function(x)spillover(x)[[3]], simplify = FALSE)
fs_comp <- compensate(fs, comp)
```

#Autoplot
```{r}
for(i in 1:length(fs)){
  print(autoplot(fs[i], x = "FSC-A", y = "SSC-A", bins = 256))
}
```

#Transform
Check the correct columns (DO NOT select FSC or SSC)
```{r}
tf <- estimateLogicle(fs_comp[[1]], channels = colnames(fs_comp[, c(5:16, 20:22, 26:31)]))
fs_trans <- transform(fs, tf)
```

##Automatic Gating till singlets
#Gating nonDebris
```{r}
gs <- GatingSet(fs_trans)
thisData <- getData(gs)
nonDebrisGate <- fsApply(thisData, function(fr)openCyto:::.flowClust.2d(fr, channels = c("FSC-H", "SSC-H")))
add(gs, nonDebrisGate, parent = "root", name = "nonDebris")
recompute(gs)
for(i in 1:length(gs)){
  print(autoplot(gs[i], x = "FSC-H", y = "SSC-H", "nonDebris", bins = 256))
}
```

#Gating singlets
```{r}
thisData <- getData(gs, "nonDebris")
singletGate <- fsApply(thisData, function(fr)openCyto:::.singletGate(fr, channels = c("FSC-H", "FSC-W")))
add(gs, singletGate, parent = "nonDebris", name = "singlets")
recompute(gs)
for(i in 1:length(gs)){
  print(autoplot(gs[i], x = "FSC-H", y = "FSC-W", "singlets", bins = 256))
}
```

#FITC
```{r}
thisData <- getData(gs, "singlets")
LinGate <- fsApply(thisData, function(fr)openCyto:::.flowClust.2d(fr, channels = c("FSC-A","FITC-A"), target = c(1.5e05, 1.5) ))
add(gs, LinGate, parent = "singlets", name = "Lin")
recompute(gs)
for(i in 1:length(gs)){
  print(autoplot(gs[i], x = "FSC-A", y = "FITC-A", "Lin", bins = 256))
}
```

#Gate SB436
```{r}
thisData <- getData(gs, "Lin")
Sca1 <- fsApply(thisData, function(fr)openCyto:::.mindensity(fr, channels = "Violet_A-A", min = 2.5 ))
add(gs, Sca1, parent = "Lin", name = "Sca1")
getNodes(gs)
recompute(gs)
getStats(gs, "Sca1", "percent")
for(i in 1:length(gs)){
  print(autoplot(gs[i], x ="Violet_A-A" , "Sca1", bins = 256))
}
```

#Gate PE
```{r}
thisData <- getData(gs, "Sca1")
F3 <- fsApply(thisData, function(fr)openCyto:::.quantileGate(fr, channels = "PE-CF594 (YG)-A"))
add(gs, F3, parent = "Sca1", name = "F3")
getNodes(gs)
recompute(gs)
getStats(gs, "F3", "percent")
for(i in 1:length(gs)){
  print(autoplot(gs[i], y = "FSC-A", x ="PE-CF594 (YG)-A", "F3", bins = 256))
}
```

#Get numbers
```{r}
getStats(gs)
```


##Manual gating for fluorescence
#Gate FITC
```{r}
LinGate <- polygonGate("FSC-A" = c(40000, 40000, 100000, 200000, 200000), "FITC-A" = c(0, 1.4, 2.2, 2.2,0))
add(gs, LinGate, parent = "singlets", name = "Lineage negative")
getNodes(gs)
recompute(gs)
for(i in 1:length(gs)){
  print(autoplot(gs[i], x = 'FSC-A', y = 'FITC-A', "Lineage negative", log = "FITC-A", bins = 256))
}
```

#gate PE and SB436
```{r}
F3 <- quadGate("PE-CF594 (YG)-A" = 2.4, "Violet_A-A"  = 2.6)
add(gs, F3, parent = "Lineage negative", name = c("Sca1+F3-", "Sca1+F3+", "Sca1- F3+", "Sca1-F3-"))
getNodes(gs)
recompute(gs)
getStats(gs, c("Sca1+F3-", "Sca1+F3+", "Sca1- F3+", "Sca1-F3-"), "percent")
for(i in 1:length(gs)){
  print(autoplot(gs[i], x = "PE-CF594 (YG)-A", y = "Violet_A-A" , c("Sca1+F3-", "Sca1+F3+", "Sca1- F3+", "Sca1-F3-"), bins = 256))
}
```
